\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-12 report/article_4.tex
report tweaks

I analysed the {\bf London house prices} dataset is several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I fit \emph{ARIMA models} to
forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, these and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Combined this set of analyses forms the basis of \logo, a
startup aimed at ``democratising real estate investment'', offering
individuals and businesses quantitative real estate insights for
data-driven investment decisions.

@@

When considering a property in a given area, you may ask a realtor
questions like: how do prices here compare to surrounding postcodes?
How have prices increased over time? And how have prices changed over
time? A real estate professional can give an opinion based on their
own limited sample size, but with a large dataset we can address these
questions quantitatively and visualise the results.

@@

Letting and sales sites may currently list some recent sales, but it's
not currently possible to see a

@@

\noindent quantitative overview of property
prices in a region, within the context of its sector, district and
postcode.

>>>>

I analysed the {\bf London house prices} dataset is several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I fit \emph{ARIMA models} to
forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, these and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Together this set of analyses forms the basis of \logo, a
startup aimed at \emph{democratising real estate investment}, offering
individuals and businesses quantitative property area insights for
data-driven investment decisions.

@@

When considering a property in a given area, you may ask a realtor
questions like: how do prices here compare to surrounding postcodes, and
how have they changed over time? A real estate professional can
give an opinion based on their own limited sample size, but with a
large dataset we can address these questions quantitatively and
visualise the results.

@@

Letting and sales sites may currently list some recent sales, but it's
not currently possible to see a quantitative overview of property
prices in a region, within the context of its sector, district and
postcode.

@@

%\noindent
